### 2017-02-12 ResearchNotes/stat_exps.tex
Adds text on statistics

\chapter{Experiments and Statistics}

% =============================================================================
\section{EXP\_001 - Plotting Activity of Students over the Semester}

>>>>

\chapter{Statistics and Experiments}

% =============================================================================
\section{Statistics}

\subsection{\texttt{STAT\_001} - Group Courses by Credits}

This experiment plots the number of courses for each possible number of credits
in a bars chart. The results of this was listed in
table~\ref{tab:courses_credits}.

\subsection{\texttt{STAT\_002} - List Domain of Courses Fields}

Gets domain of the fields of courses. Relevant results are listed in some
tables in section~\ref{sec:data_courses}.

% =============================================================================
\section{Experiments}

\subsection{\texttt{EXP\_001} - Plotting Activity of Students over the
Semester}
